% Anne of Green Gables from Project Gutenberg:
% https://www.gutenberg.org/cache/epub/45/pg45-images.html
% Excerpts from Chapter 3, Marilla Cuthbert Is Surprised
\documentclass[a4paper]{article}

\title{Anne of Green Gables}
\author{Lucy Maud Montgomery}
\date{06/13/1908}

\begin{document}
\maketitle

% Single italic word
The word \itshape ``italics'' \upshape is italicized in this sentence. By italicizing the word ``italics,'' \LaTeX renders it autologically. An autological word possesses or demonstrates what it describes. Apparently, a word exists for almost everything!

% Single italic word in a block
The word {\itshape ``italics''} is italicized in this sentence. By italicizing the word ``italics,'' \LaTeX renders it autologically. An autological word possesses or demonstrates what it describes. Apparently, a word exists for almost everything!

% Multiple italic words
Regular, non-italicized text begins this sentence. \itshape However, the second sentence is italicized for dramatic effect. \upshape In stark contrast, this paragraph  concludes with another sentence in boring, regular text.

% Multiple italic words in a block
Regular, non-italicized text begins this sentence. {\itshape However, the second sentence is italicized for dramatic effect.} In stark contrast, this paragraph concludes with another sentence in boring, regular text.

% Italic paragraph
\itshape In addition to single words and single sentences, an entire paragraph can be italicized. Sadly, nothing in this paragraph warrants the extra emphasis from italics; these trivial words only exist for \LaTeX to exhibit its rendering engine. \upshape

% Italic paragraph in a block
{\itshape In addition to single words and single sentences, an entire paragraph can be italicized. Sadly, nothing in this paragraph warrants the extra emphasis from italics; these trivial words only exist for \LaTeX to exhibit its rendering engine.}

% Multiple italic paragraphs
\itshape All paragraphs of this example are italicized. In CSS, font-style controls the slanting of the text. The value ``italic'' italicizes the text, and the value ``normal'' yields regular text.

CSS has another font-style value, ``oblique,'' which supports slant values in degrees. If no font classified as oblique is listed in the font-family, then a font classified as italic is substituted. The converse is also possible, which means oblique and italic are somewhat interchangeable in CSS. \upshape

% Multiple italic paragraphs in a block
{\itshape All paragraphs of this example are italicized. In CSS, font-style controls the slanting of the text. The value ``italic'' italicizes the text, and the value ``normal'' yields regular text.

CSS has another font-style value, ``oblique,'' which supports slant values in degrees. If no font classified as oblique is listed in the font-family, then a font classified as italic is substituted. The converse is also possible, which means oblique and italic are somewhat interchangeable in CSS.}

% Chapter 3, Marilla Cuthbert Is Surprised

% Single italic word
Marilla set the \itshape candle \upshape on a three-legged, three-cornered table and turned down the bedclothes.

% Single italic word in a block
``I suppose you have a {\itshape nightgown?}'' she questioned.

Anne nodded.

% Multiple italic words
``Yes, I have two. The matron of the asylum made them for me. They're fearfully skimpy. There is never enough to go around in an asylum, so things are always skimpy---at least in a poor asylum like ours. \itshape I hate skimpy night-dresses. \upshape But one can dream just as well in them as in lovely trailing ones, with frills around the neck, that's one consolation.''

% Multiple italic words in a block
``Well, undress as quick as you can and go to bed. I'll come back in a few minutes for the candle. {\itshape I daren't trust you to put it out yourself.} You'd likely set the place on fire.''

% Italic paragraph
\itshape When Marilla had gone Anne looked around her wistfully. The whitewashed walls were so painfully bare and staring that she thought they must ache over their own bareness. The floor was bare, too, except for a round braided mat in the middle such as Anne had never seen before. In one corner was the bed, a high, old-fashioned one, with four dark, low-turned posts. In the other corner was the aforesaid three-cornered table adorned with a fat, red velvet pincushion hard enough to turn the point of the most adventurous pin. Above it hung a little six-by-eight mirror. Midway between table and bed was the window, with an icy white muslin frill over it, and opposite it was the wash-stand. The whole apartment was of a rigidity not to be described in words, but which sent a shiver to the very marrow of Anne's bones. With a sob she hastily discarded her garments, put on the skimpy nightgown and sprang into bed where she burrowed face downward into the pillow and pulled the clothes over her head. When Marilla came up for the light various skimpy articles of raiment scattered most untidily over the floor and a certain tempestuous appearance of the bed were the only indications of any presence save her own. \upshape

% Italic paragraph in a block
{\itshape She deliberately picked up Anne's clothes, placed them neatly on a prim yellow chair, and then, taking up the candle, went over to the bed.}

% Multiple italic paragraphs
\itshape ``Good night,'' she said, a little awkwardly, but not unkindly.

Anne's white face and big eyes appeared over the bedclothes with a startling suddenness.

``How can you call it a good night when you know it must be the very worst night I've ever had?'' she said reproachfully.

Then she dived down into invisibility again. \upshape

% Multiple italic paragraphs in a block
{\itshape Marilla went slowly down to the kitchen and proceeded to wash the supper dishes. Matthew was smoking---a sure sign of perturbation of mind. He seldom smoked, for Marilla set her face against it as a filthy habit; but at certain times and seasons he felt driven to it and then Marilla winked at the practice, realizing that a mere man must have some vent for his emotions.

``Well, this is a pretty kettle of fish,'' she said wrathfully. ``This is what comes of sending word instead of going ourselves. Richard Spencer's folks have twisted that message somehow. One of us will have to drive over and see Mrs. Spencer tomorrow, that's certain. This girl will have to be sent back to the asylum.''

``Yes, I suppose so,'' said Matthew reluctantly.}

\end{document}