% Anne of Green Gables from Project Gutenberg:
% https://www.gutenberg.org/cache/epub/45/pg45-images.html
% Excerpts from Chapter 6, Marilla Makes Up Her Mind
\documentclass[a4paper]{article}

\title{Anne of Green Gables}
\author{Lucy Maud Montgomery}
\date{06/13/1908}

\begin{document}
\maketitle

% Chapter 6, Marilla Makes Up Her Mind

% Blocks around switches
% Switches around paragraphs
% Commands within switches
% Switches within commands

``I'll try to do and be anything you want me, if you'll only keep me,'' said Anne, returning meekly to her ottoman.

When they arrived back at Green Gables that evening Matthew met them in the lane. Marilla from afar had noted him prowling along it and guessed his motive. She was prepared for the relief she read in his face when he saw that she had at least brought Anne back with her. But she said nothing, to him, relative to the affair, until they were both out in the yard behind the barn milking the cows. Then she briefly told him Anne's history and the result of the interview with Mrs. Spencer.

``I wouldn't give a dog I liked to that Blewett woman,'' said Matthew with unusual vim.

``I don't fancy her style myself,'' admitted Marilla, ``but it's that or keeping her ourselves, Matthew. And, since you seem to want her, I suppose I'm willing---or have to be. I've been thinking over the idea until I've got kind of used to it. It seems a sort of duty. I've never brought up a child, especially a girl, and I dare say I'll make a terrible mess of it. But I'll do my best. So far as I'm concerned, Matthew, she may stay.''

Matthew's shy face was a glow of delight.

``Well now, I reckoned you'd come to see it in that light, Marilla,'' he said. ``She's such an interesting little thing.''

``It'd be more to the point if you could say she was a useful little thing,'' retorted Marilla, ``but I'll make it my business to see she's trained to be that. And mind, Matthew, you're not to go interfering with my methods. Perhaps an old maid doesn't know much about bringing up a child, but I guess she knows more than an old bachelor. So you just leave me to manage her. When I fail it'll be time enough to put your oar in.''

``There, there, Marilla, you can have your own way,'' said Matthew reassuringly. ``Only be as good and kind to her as you can without spoiling her. I kind of think she's one of the sort you can do anything with if you only get her to love you.''

Marilla sniffed, to express her contempt for Matthew's opinions concerning anything feminine, and walked off to the dairy with the pails.

``I won't tell her tonight that she can stay,'' she reflected, as she strained the milk into the creamers. ``She'd be so excited that she wouldn't sleep a wink. Marilla Cuthbert, you're fairly in for it. Did you ever suppose you'd see the day when you'd be adopting an orphan girl? It's surprising enough; but not so surprising as that Matthew should be at the bottom of it, him that always seemed to have such a mortal dread of little girls. Anyhow, we've decided on the experiment and goodness only knows what will come of it.''

CHAPTER VII.
Anne Says Her Prayers
WHEN Marilla took Anne up to bed that night she said stiffly:

``Now, Anne, I noticed last night that you threw your clothes all about the floor when you took them off. That is a very untidy habit, and I can't allow it at all. As soon as you take off any article of clothing fold it neatly and place it on the chair. I haven't any use at all for little girls who aren't neat.''