% Anne of Green Gables from Project Gutenberg:
% https://www.gutenberg.org/cache/epub/45/pg45-images.html
% Excerpts from Chapter 3, Marilla Cuthbert Is Surprised
\documentclass[a4paper]{article}

\title{Anne of Green Gables}
\author{Lucy Maud Montgomery}
\date{06/13/1908}

\begin{document}
\maketitle

% Bold word in a paragraph
This is a sentence with a \bfseries bold \mdseries word in it. The rest of this paragraph renders in regular weight text. Finally, the quick brown fox jumps over the lazy dog to encourage word wrap.

% Bold word in a paragraph in a block
This is a sentence with a {\bfseries bold} word in it. The rest of this paragraph renders in regular weight text. Finally, the quick brown fox jumps over the lazy dog to encourage word wrap.

% Multiple bold words in a paragraph
Regular weight text begins this sentence, but \bfseries bold text concludes it. \mdseries This paragraph ends with regular weight text. This sentence rounds out the paragraph so LaTeX renders 3 lines.

% Multiple bold words in a paragraph in a block
Regular weight text begins this sentence, but {\bfseries bold text concludes it.} This paragraph ends with regular weight text. This sentence rounds out the paragraph so LaTeX renders 3 lines.

% Bold paragraph
\bfseries This entire paragraph is bold, from the very beginning to the bitter end. The bold middle sentence adds heft to the paragraph. The last sentence rounds out the verbose nothingness. \mdseries

% Bold paragraph in a block
{\bfseries This entire paragraph is bold, from the very beginning to the bitter end. The bold middle sentence adds heft to the paragraph. The last sentence rounds out the verbose nothingness.}

% Multiple bold paragraphs
\bfseries Here is the first bold paragraph. In CSS, font-weight controls degrees of boldness, but the various fonts listed for font-family determine which values are actually available. A fallback algorithm selects substitutions for unsupported font-weight values.

This is the second bold paragraph, and it details nothing further about CSS's font-weight. It contains some superfluous sentences and much ado about nothing. When this paragraph concludes, all the examples are finished, too. \mdseries

% Multiple bold paragraphs in a block
{\bfseries Here is the first bold paragraph. In CSS, font-weight controls degrees of boldness, but the various fonts listed for font-family determine which values are actually available. A fallback algorithm selects substitutions for unsupported font-weight values.

This is the second bold paragraph, and it details nothing further about CSS's font-weight. It contains some superfluous sentences and much ado about nothing. When this paragraph concludes, all the examples are finished, too.}

% Chapter 3, Marilla Cuthbert Is Surprised

% Bold word in a paragraph
``No. We want a boy to help Matthew on the farm. A \bfseries girl \mdseries would be of no use to us. Take off your hat. I'll lay it and your bag on the hall table.''

% Bold word in a paragraph in a block
Anne took off her hat meekly. Matthew came back presently and they sat down to supper. But Anne could not eat. In vain she nibbled at the bread and butter and pecked at the {\bfseries crab-apple} preserve out of the little scalloped glass dish by her plate. She did not really make any headway at all.

% Multiple bold words in a paragraph
\bfseries ``You're not eating anything,''\mdseries said Marilla sharply, eying her as if it were a serious shortcoming. Anne sighed.

% Multiple bold words in a paragraph in a block
``I can't. {\bfseries I'm in the depths of despair.} Can you eat when you are in the depths of despair?''

% Bold paragraph
\bfseries ``I've never been in the depths of despair, so I can't say,'' responded Marilla.\mdseries

% Bold paragraph in a block
{\bfseries ``Weren't you? Well, did you ever try to imagine you were in the depths of despair?''}

% Multiple bold paragraphs
\bfseries ``No, I didn't.''

``Then I don't think you can understand what it's like. It's a very uncomfortable feeling indeed. When you try to eat a lump comes right up in your throat and you can't swallow anything, not even if it was a chocolate caramel. I had one chocolate caramel once two years ago and it was simply delicious. I've often dreamed since then that I had a lot of chocolate caramels, but I always wake up just when I'm going to eat them. I do hope you won't be offended because I can't eat. Everything is extremely nice, but still I cannot eat.''\mdseries

% Multiple bold paragraphs in a block
{\bfseries ``I guess she's tired,'' said Matthew, who hadn't spoken since his return from the barn. ``Best put her to bed, Marilla.''

Marilla had been wondering where Anne should be put to bed. She had prepared a couch in the kitchen chamber for the desired and expected boy. But, although it was neat and clean, it did not seem quite the thing to put a girl there somehow. But the spare room was out of the question for such a stray waif, so there remained only the east gable room. Marilla lighted a candle and told Anne to follow her, which Anne spiritlessly did, taking her hat and carpet-bag from the hall table as she passed. The hall was fearsomely clean; the little gable chamber in which she presently found herself seemed still cleaner.}

\end{document}